---
title             : "An Attempt at Collaboration with GitKraken"
shorttitle        : "Lab 8"
author:
  - name          : "Akhila Nekkanti"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Center for Translational Neuroscience University of Oregon 1585 E 13th Ave. Eugene, OR 97403"
    email         : "akhilan@uoregon.edu"
  - name         : "Kyle Reardon"
    affiliation   : "1"
    corresponding : no
  - name          : "Brock Rowley"
    affiliation   : "1"
    corresponding : no
  - name          : "Jeff Gau"
    affiliation   : "1"
    corresponding : no

affiliation:
  - id            : "1"
    institution   : "University of Oregon"
    
author note: |
  First authosgs.hmstrljh
    
abstract: |
  This is our abstract and it's really something else! SO abstract! And so concise! 
  
keywords          : "add, some, keywords, words, keys, Yo, Key, Word"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      fig.width = 6.5, 
                      fig.height = 8)

library(rio)
library(here)
library(tidyverse)
library(janitor)
library(tinytex)
library(devtools)
library("papaja")

```


```{r import_data}
star <- import(here("data", "star.csv")) %>%  
        janitor::clean_names()

ggplot(star, aes(totexp, tmathss)) +
  geom_point(color = "gray70") +
  geom_smooth(method = "lm", se = TRUE, aes(color = frl)) +
  labs(x = "Teacher Experience (years)", 
       y = "Total Math Scale Score",
       title = "Relation between teacher experience and math scores",
       subtitle = "Separate regression lines displayed by free/reduced price lunch status") +
  guides(color = guide_legend(reverse = TRUE)) +
  theme(legend.position = "bottom") +
  scale_fill_discrete(breaks=c("no","yes")) +
  scale_color_manual(name="Lunch status", 
                        labels = c("Paid Meals", "Free/Reduced Price Meals"),
                        values = c("no"="firebrick3", 
                                   "yes"="aquamarine3"))
 
```

@wehman2014 conducted a case study to examine the the effect of supported employment on vocational rehabilitation outcomes of transition-age youth. Other researchers examined various pathways to employment in adults with disabilities [siperstein2014pathways].

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results
Table 1 demonstrates the relationship between teacher experience and student's math scale scores. The two regression lines demonstrate differences between free and reduced price lunch status, which students who are not eligible for free and reduced price lunch scoring, in general, higher than those who do. In general, it does not appear that teacher experience significantly impacts this difference, as math scores for students both with and without free and reduced price lunch status appears to increase at approximately the same rate.

# Discussion


\newpage
# Table 1
```{r}

```

\newpage
# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
